---
title             : "Engagement Measurment of Invariance"
shorttitle        : "Title"

author: 
  - name          : "Casey Osorio-Duffoo"
    affiliation   : "1"
    corresponding : yes    
    address       : "Postal address"
    email         : "caseyosorio@gmail.com"
    role:         
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Morgan Russell"
    affiliation   : "2"
    role:
      - Writing - Review & Editing
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "3"
    role:
      - Conceptualization
      - Writing - Review & Editing
  - name          : "John Kulas"
    affiliation   : "4"
    role:
      - Conceptualization
      - Writing - Review & Editing
    
affiliation:
  - id            : "1"
    institution   : "Harver"
  - id            : "2"
    institution   : "Montclair State University"
  - id            : "3"
    institution   : "Montclair State University"
  - id            : "4"
    institution   : "Montclair State University"
    

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "engage.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


## Definitions of Engagement

The roots of employee [aka work; e.g., @schaufeli_conceptualization_2010] engagement research likely started with theoretical expansions of forms of employee participation [see, for example, @ferris_added_1984] and job involvement [e.g., @elloy_examination_1991]. This exploration extended into broader considerations of attitudes and emotions [@staw_employee_1994] and were informed by further exploration of the dimensionality of constructs such as organizational commitment [@meyer_three-component_1991]. The 1990's saw focused development and refinement (for example, a dissertation; @leone_relation_1995 or actual semantic reference; @kahn_psychological_1990). @staw_employee_1994 investigated the  relationships between *positive emotions* and favourable work outcomes, and although they do not use the word, "engagement", their distinction between felt and expressed emotion was likely a stimulating influence upon the burgeoning interest in the engagement construct. Gallup is also widely acknowledged as an early pioneer in the measurement of the construct [see, for example, @coffman_hard_1999]. 

@kahn_psychological_1990 described engaged employees as being physically involved, cognitively vigilant, and emotionally connected. Although occasionally referred to as residing on the opposing pole to *burnout* [@maslach_early_2008], these two constructs are currently most commonly conceptualized as being distinct [@timms2012burnt], although not universally [@cole2012job; @taris2017burnout].  

+ Engagement/Burnout: Burnout is defined as a psychological syndrome          characterized by           exhaustion, cynicism, and inefficacy, which is     experienced in response to chronic job         stressors. Engagement is       understood to be the direct opposite of burnout and exist on a                continuum—with engagement on one end and burnout on the other. Exhaustion     (low energy),       cynicism (low involvement), and inefficacy (low           efficacy) are characteristic of burnout;      whereas, high energy, high      involvement, and high efficacy are characteristic of engagement @maslach1997causes   (Maslach   and Leiter, 1997) [@leiter_areas_2004].
+ Work engagement: Work engagement refers to a positive, fulfilling, work-related state of      mind that is characterized by vigor, dedication, and absorption. Vigor is characterized by    high levels of energy and mental resilience while working. Dedication refers to being         strongly involved in one’s work and experiencing a sense of significance, enthusiasm,         inspiration, pride, and challenge. Absorption is characterized by being fully concentrated    and happily engrossed in one’s work, whereby time passes quickly and one has difficulties     with detaching oneself from work [@schaufeli_measurement_2002] - The Utrecht Work Engagement       Scale (UWES), a self-report questionnaire first developed by Schaufeli and Bakker (2003)   [@schaufeli_uwesutrecht_2003]   includes the three aspects of work engagement: vigor, dedication, and absorption. - we have   to make note of how we are different from this! 
+ Employee engagement:  Employee engagement refers to the ‘‘individual’s involvement and        satisfaction as well as enthusiasm for work’’ [@harter_business-unit-level_2002]
  Work engagement is the mental state where employees...  


+ ...feel full with physical energy (**Vigor**)
+ ...are enthusiastic about the content of their work and the things they do (**Dedication**)
+ ...are so immersed in their work activities that time seems to fly (**Absorption**)

The tripartite substantive model of employee engagement is also partially informed by the definitions provided with the Utrecht Work Engagement Scale [@schaufeli_utrecht_2003].


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
